Incentivizing Exploration with Unbiased History

### 2018-10-09 2level.tex
comments

For each arm $a$, define $q_a$ to be the expected number of arm $a$ pulls in one run of \ALGG used in the first level. By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$. Define $W_1^a$ to be the event that the number of arm $a$ pulls in the first level is at least $q_a T_1- \GdT \sqrt{T_1\log(T)} \geq q_a T_1 / 2$. By Chernoff bound,
\[
\Pr[W_1^a] \geq 1-\exp(-2\log(T)) \geq 1-1/T^2.
\]
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a}W_1^a$). By union bound, we have
\[
\Pr[W_1] \geq 1- \frac{K}{T^2} \geq 1 - \frac{1}{T}.
\]
\item  \textbf{Concentration of the empirical mean of arm $a$ pulls in the first level:}

@@

Notice that if we know the gap between the means of the best arm and second best arm is larger than $\Delta$, we can set 
\[
T_1 = \max\left( \frac{4\GdT^2}{\GdP^2}\log(T), \frac{36 }{\Delta^2 \cdot p_G} \log(T) \right).
\]
In this case, since $\Delta \geq 6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$, we know agents in the second level will all pull arm 1. Therefore, the total expected regret is at most
\[
T_1 \cdot \GdT + T \cdot (1- \Pr[W_1 \cap W_2]) = O(\Delta^{-2} \log(T)).
\]
\end{proof}

>>>>

  For each arm $a$, define $q_a$ to be the expected number of arm $a$
  pulls in one run of \ALGG used in the first level.\swcomment{$q_a$
    probability or number?? the issue propagates downwards} By Lemma
  \ref{lem:greedy}, we know $\GdP \leq q_a \leq
  \GdT$.\swcomment{$p_G T$?} Define $W_1^a$ to be the event that the
  number of arm $a$ pulls in the first level is at least
  $q_a T_1- \GdT \sqrt{T_1\log(T)} \geq q_a T_1 / 2$.\swcomment{what
    is the condition on $T_1$ and $T_G$ for this to hold?} By Chernoff
  bound,
\[
\Pr[W_1^a] \geq 1-\exp(-2\log(T)) \geq 1-1/T^2.
\]
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a}W_1^a$). By union bound, we have
\[
\Pr[W_1] \geq 1- \frac{K}{T^2} \geq 1 - \frac{1}{T}.
\]
\item  \textbf{Concentration of the empirical mean of arm $a$ pulls in the first level:}

@@

Notice that if we know the gap between the means of the best arm and second best arm is larger than $\Delta$, we can set 
\[
T_1 = \max\left( \frac{4\GdT^2}{\GdP^2}\log(T), \frac{36 }{\Delta^2 \cdot p_G} \log(T) \right).
\]
In this case, since $\Delta \geq 6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$, we know agents in the second level will all pull arm 1. Therefore, the total expected regret is at most
\[
T_1 \cdot \GdT + T \cdot (1- \Pr[W_1 \cap W_2]) = O(\Delta^{-2} \log(T)).
\]
\end{proof}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
